\documentclass[10pt]{resume}

\name{Archim Jhunjhunwala}
\usepackage{enumitem}

\address{22 Beacon Heights Dr.\\ Newton, Massachusetts 02459}
\address{(857)~$\cdot$~636~$\cdot$~0914 \\ archimj@proton.me \\ github.com/hfytr }
\newenvironment{rlist}{
  \begin{itemize}{\leftmargin=0em}
  \itemsep -0.5em \vspace{-0.5em}
  }{\end{itemize}}
\newenvironment{rindentList}{\begin{rlist}}{}

\begin{document}

\begin{rSection}{Education}
    \textbf{Homeschool GPA: 3.9} \\
    \textbf{AP Courses}
    \begin{rlist}
        \item Calculus BC, Computer Science A, Statistics
        \item Physics C Mechanics, Physics C E\&M, Chemistry
    \end{rlist}
    \textbf{Undergraduate and Graduate Classes}
    \begin{rlist}
        \item Real Analysis, Compilers, Operating Systems (ongoing),
            Differential Equations (ongoing), Discrete Mathematics, Linear /
            Integer Programming, Linear Algebra 
    \end{rlist}
\end{rSection}

\begin{rSection}{Research Projects}
    \textbf{AC Optimal Power Flow} \hfill \textit{June 2025 - Present} \\
    \textit{Shin Group, MIT Chemical Engineering} \\
    Part of a group developing algorithms to solve Alternating Current Optimal
    Power Flow (ACOPF) problems on international grid scale. ACOPF problems
    face real world issues like downage of power-lines, and mathematical ones
    such as non-convexity and non-linearity. Culminated in presentation to
    group, as well as HIP-SAT symposium.
    \begin{rlist}
        \item Leveraged and contributed to ExaModels.jl, a GPU based NLP solver
            utilizing KKT methods.
        \item Contributed to security constrained, multi-period, and static
            ACOPF formulations.
        \item Independently developed ExaPowerIO.jl, a tool for data parsing
            40x faster than alternatives. Data previously represented up to
            70\% of problem runtime.
    \end{rlist}

    \textbf{Political Districting} \hfill \textit{June 2024 - November 2024}\\ 
    \textit{Sankarnarayanan Group, University of Colorado, Boulder} \\
    Created optimally unbiased political districts using a combination of Mixed
    Integer Linear Programming, and Simulated Annealing. Also devised metrics
    to accurately measure compactness / fairness of political districts, an
    inherently subjective trait.
    \begin{rlist}
        \item Created ML models to estimate compactness / fairness of political
            districts using Neural Networks, and various other regression
            techniques.
        \item Wrote a performant, customized Simulated Annealer from scratch in
            order to search the space of possible districting plans.
        \item Used MILP as a projection operator to ensure feasability of
            generated districts.
    \end{rlist}
\end{rSection}

\begin{rSection}{Independent Projects}
    These are smaller projects taken on purely for learning purposes. They are
    done in my spare time over a period of 1-6 months (although some are
    longer).
    \begin{rlist}
        \item An LSP for Julia (ongoing), including a compile-time LALR(1)
            parser generator and regex engine.
        \item Various contributions to the Wideriver tiling window manager.
        \item A lightweight, terminal-based, reading interface for the website
            Royal Road. I use this daily.
        \item Feed forward neural network from scratch. Got 95\% accuracy on
            MNIST.
        \item A negamax chess engine rated 2500 elo based on play with other
            engines.
        \item A CPU ray tracer supporting .obj files.
        \item Participated in various hackathons. Won \$2000 total.
    \end{rlist}
\end{rSection}

\begin{rSection}{Technical Skills}
    \begin{itemize}[leftmargin=*]
        \item Rust, C, Julia, C++, Haskell, Python
        \item Functional Analysis, Mixed Integer Linear Programming, Non-Linear
        Programming, GPU Based Optimization
    \end{itemize}
\end{rSection}
\end{document}
